Graphical Tests for Power Comparison of Competing Designs

### 2012-03-29 setup.tex
tweaking setup

% !TEX root = comparison.tex
\section{Experimental Setup}~\label{experimentone}
We want two discuss two applications, in which we are making use of lineups to compare competing designs. 
The first one arises from a discussion of how wind direction affects efficiency of an airport. in the second example we are interested in visualizing mean shifts between two distributions.

>>>>

% !TEX root = comparison.tex
\section{Experimental Setup}~\label{experimentone}

Two recent data analyses motivated the setup of this experiment. The
first one arises from an analysis of US flight traffic data, and a
finding related to how wind direction affects the efficiency of an
airport.  The second one arose during the review of a paper claiming
that it was impossible to statistically test for differences in center
between two samples where sample size was small and from a non-normal
population, with application to studying toxic waste sites. Visually,
using lineups of dotplots, it was clear that there was a difference.

%We want two discuss two applications, in which we are making use of lineups to compare competing designs. in the second example we are interested in visualizing mean shifts between two distributions.
